### 2025-06-22 conteudo/introduction/intro.tex
Update intro.tex

Beyond detection, we also investigated if the duplications found by ArKanjo could be mitigated.
This was achieved through an ethnographic approach, which included a participant observation 
study where we attempted to mitigate duplications, and a non-participant observation study of 
university students tasked with fixing duplications found by the tool. These studies showed that 
ArKanjo can effectively lower the barrier for new contributors, as evidenced by its role in 
guiding students to make their first code improvements to the kernel.

>>>>

Beyond detection, we also investigated if the duplications found by ArKanjo could be mitigated.
This was achieved through an ethnographic approach, which included a participant observation 
study where we attempted to mitigate duplications, and a non-participant observation study of 
university students tasked with fixing duplications found by the tool. These studies showed that 
ArKanjo can effectively lower the barrier for new contributors, as evidenced by its role in 
guiding students to make their first code contributions to the kernel.
